Very simplified likelihood

### 2024-02-11 inst/very_simplified_likelihood.Rmd
streamlining

```{r calculatelikes,cache=TRUE}
a <- seq(from=0.15,to=0.5,by=0.01)
La <- L(a,results)
La <- La-max(La,na.rm=TRUE)
La2 <- f_vec_arn(a,r=results$place-1,results$runners-1,log=TRUE)
La2 <- La2 - max(La2,na.rm=TRUE)
```

```{r plotlike}
plot(a,La)
points(a,La2)
abline(h=c(0,-2))
```

```{r optimsinglelike}
optimize(function(a){L(a,results)},c(0.3,0.4),maximum=TRUE)
```

@@

```{r, label=onedimopt}
f <- function(a){supp2(c(a,a),results$place,results$runners)}
a <- seq(from=0.1,to=0.6,by=0.05)
alike <- sapply(a,f)
plot(a,alike,type='b')
optimize(f,c(0.1,0.6),maximum=TRUE)
```

@@

```{r,label=showchisquareasymptotic}
pchisq(2*(7381.496-7380.314),df=1,lower.tail=FALSE)
```

>>>>

```{r calculatelikes,cache=TRUE}
a <- seq(from=0.15,to=0.5,by=0.01)
La <- f_vec_arn(a,r=results$place-1,results$runners-1,log=TRUE)
La <- La - max(La,na.rm=TRUE)
```

```{r plotlike}
plot(a,La)
abline(h=c(0,-2))
```

```{r optimsinglelike}
optimize(function(a){L(a,results)},c(0.2,0.4),maximum=TRUE)
```

```{r calculatelikes1,cache=TRUE}
a <- seq(from=0.005,to=0.6,by=0.005)
La <- f_vec_arn(a,r=results$place[1]-1,results$runners[1]-1,log=TRUE)
La <- La - max(La,na.rm=TRUE)
plot(a,La,type='b')
abline(h=c(0,-2))
```

@@

```{r, label=onedimopt}
f <- function(a){supp2(c(a,a),results$place,results$runners)}
a <- seq(from=0.1,to=0.45,by=0.01)
alike <- sapply(a,f)
plot(a,alike-max(alike,na.rm=TRUE),type='b')
abline(h=c(0,-2))
optimize(f,c(0.1,0.6),maximum=TRUE)
```

@@

```{r,label=showchisquareasymptotic}
7380.314-7381.496
pchisq(2*(7381.496-7380.314),df=1,lower.tail=FALSE)
```
